\subsection{Link Budget}
\paragraph
\
The link budget calculations are mostly calculated using the following fonts:\cite{linkBudget}
\subsubsection{Communications Basics}
\paragraph
\
\cite{an9804.pdf}
When evaluating a wireless link, the three most important questions to be answered are:\\
\begin{enumerate}
	\item How much radio frequency (RF) power is available?
	\item How much bandwidth is available?
	\item What is the rquired reliability (as defined by Bit Error Rate, or BER)?
\end{enumerate}

The upper limit in terms of data rate is given by Shannon's Channel Capacity Theorem:
\begin{equation}
	C=Blog_2(1+S/N)
	\label{channelCapacity}
\end{equation}
where:
\begin{align*}
	C&= \text{channel capacity (bits/s)}\\
	B&= \text{channel bandwidth (Hz)}\\
	S&= \text{signal strength (watts)}\\
	N&= \text{noise power (watts)}
\end{align*}

\subsubsection{Channel Noise}
\paragraph
\
All objects which have heat emit RF energy in the form of random (Gaussian) noise. The amount of radiation emitted can be calculated by \cite{linkBudget}:
\begin{equation}
	N=kTB
	\label{noise}
\end{equation}
where:
\begin{align*}
	N&= \text{noise power (watts)}\\
	k&= \text{Boltzman's constant}(1.38\mathrm{x}10^{-23}J/K)\\
	T&= \text{system temperature, usually assumed to be 290K}\\
	B&= \text{channel bandwidth (Hz)}
\end{align*}

This is the lowest possible noise level for a system with a given physical temperature. For most applications, temperature is typically assumed to be room temperature (290K). Equations \ref{channelCapacity} and \ref{noise} demonstrate that RF power and bandwidth can be traded off to achieve a given performance level (as defined by BER).

\subsubsection{Range and Path Loss}
Another key consideration is the issue of range. As radio
waves propagate in free space, power falls off as the square
of range. For a doubling of range, power reaching a receiver
antenna is reduced by a factor of four. This effect is due to
the spreading of the radio waves as they propagate, and can
be calculated by:
\begin{equation}
	L=20log_{10}(4\pi D/\lambda)
\end{equation}
where:
\begin{align*}
	D&= \text{the distance between receiver and transmitter}\\
	\lambda&= \text{free space wavelength = c/f}\\
	c&= \text{speed of light}(3\mathrm{x}10^8m/s)\\
	f&= \text{frequency (Hz)}
\end{align*}

\subsubsection{Ling budget calculation}
$EIRP=P_T-L_T-G_T$
